Crop adaptation through gene flow

### 2016-07-10 Crop_adaptation_gene_flow_gj_outline_shortened.tex
Update Crop_adaptation_gene_flow_gj_outline_shortened.tex

However, comparative isozyme analyses \cite{shechter1975comparative}\ have suggested a possible secondary domestication event (sorghum race kafir) in the southeastern Savanna.s
The progenitor species was \emph{S. arundinaceum} \cite{doggett1988sorghum, harlan1971toward}\.
The genus Sorghum contains 25 species, but these are split between five subgenera: Eu-Sorghum, Chaetosorghum, Heterosorghum, Para-Sorghum, and Stiposorghum, and it is Eu-Sorghum that includes all domesticated, weedy, and closely-related wild relatives \cite{USDAARS2007, garber1950cytotaxonomic}.

>>>>

However, comparative isozyme analyses \cite{shechter1975comparative}\ have suggested a possible secondary domestication event (sorghum race kafir) in the southeastern Savanna.
The progenitor species was \emph{S. arundinaceum} \cite{doggett1988sorghum, harlan1971toward}\.
The genus Sorghum contains 25 species, but these are split between five subgenera: Eu-Sorghum, Chaetosorghum, Heterosorghum, Para-Sorghum, and Stiposorghum, and it is Eu-Sorghum that includes all domesticated, weedy, and closely-related wild relatives \cite{USDAARS2007, garber1950cytotaxonomic}.
